More than one Author with different Affiliations

### 2016-02-25 NatPlant2/manuscript.tex
updates

Because our modest sample size of fully sequenced individuals has limited power to infer recent population expansion, we investigated two alternative approaches for demographic inference.  
First, we utilized genotyping data from more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize effective population size.
Because rare variants provide the best information about recent effective population sizes \cite{keinan2012}, we estimate $N_e$ using  a singleton-based estimator \cite{fu1993} of the population mutation rate $\theta=4N_e\mu$  and published values of the mutation rate \cite{clark2005} (see online methods for details). 
This yields a much higher estimate of the modern maize effective population size at  $N_m \approx 993,000$.
Finally, we employed a model-free coalescent approach \cite{schiffels2014} to estimate population size change using a subset of six genomes each of maize and teosinte.
Though this analysis suggests non-equilibrium dynamics for teosinte not included in our initial model, it is nonetheless broadly consistent, identifying a clear domestication bottleneck followed by rapid population expansion in maize to an extremely large extant size of $\approx 10^9$ (Figure \ref{sFig:msmc}).
Our assessment of the historical demography of maize and teosinte provides context for subsequent analyses of linked selection.

@@

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (\url{http://lh3lh3.users.sourceforge.net/snpable.shtml}). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameters $20\times2+20\times4+10\times2$.

>>>>

Because our modest sample size of fully sequenced individuals has limited power to infer recent population expansion, we investigated two alternative approaches for demographic inference.  
First, we utilized genotyping data from more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize effective population size.
Because rare variants provide the best information about recent effective population sizes \cite{keinan2012}, we estimate $N_e$ using  a singleton-based estimator \cite{fu1993} of the population mutation rate $\theta=4N_e\mu$  and published values of the mutation rate \cite{clark2005} (see online methods for details). 
This yields a much higher estimate of the modern maize effective population size at  $N_m \approx 993,000$.
Finally, we employed a model-free coalescent approach \cite{schiffels2014} to estimate population size change using a subset of six genomes each of maize and teosinte.
Though this analysis suggests non-equilibrium dynamics for teosinte not included in our initial model, it is nonetheless broadly consistent with the other approaches, identifying population isolation beginning between 10,000 and 15,000 generations ago, a clear domestication bottleneck, and ultimately rapid population expansion in maize to an extremely large extant size of $\approx 10^9$ (Figure \ref{sFig:msmc}).
Our assessment of the historical demography of maize and teosinte provides context for subsequent analyses of linked selection.

@@

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (\url{http://lh3lh3.users.sourceforge.net/snpable.shtml}). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameter $20\times2+20\times4+10\times2$ (Figure \ref{sFig:msmc}A) for population size inference. To estimate the rate of cross-coalescence we used four maize and four teosinte haplotypes with pattern parameter $20\times1 + 20\times2$ (Figure \ref{sFig:msmc}B).

### 2016-02-25 NatPlant2/supportingInfo.tex
updates

\begin{figure}
  \begin{center}
    \includegraphics[width=.85\textwidth]{FigsAndFiles/TIL_BKN_bootstrapping_msmc.pdf}
    \end{center}
\caption{Effective population size estimated over time using MSMC. Shown are estimates (solid lines) and boostrap resampling (dotted lines) for both maize (red) and teosinte (blue). Time is estimated assuming an annual generation time and a mutation rate of $\mu=3\times 10^{-8}$ \label{sFig:msmc}}
\end{figure}
\clearpage

>>>>

\begin{figure}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/TIL_BKN_bootstrapping_msmc2_labeled.pdf}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/relativeCrossCoalescenceRate_labeled.pdf}
\caption{MSMC Analyses. Shown in \textbf{A} are effective population size estimates over time. Estimates are depicted as solid lines and boostrap resampling is represented with dotted lines for both maize (red) and teosinte (blue). \textbf{B} depticts the cross-coalescence rate between maize and teosinte estimated using MSMC. In both panels, time is estimated assuming an annual generation time and a mutation rate of $\mu=3\times 10^{-8}$ \label{sFig:msmc}}
\end{figure}
\clearpage
